# Deliverables Schedule  {.unnumbered}

```{r,include=FALSE,results='hide'}
library(odbc)
library(tidyverse)

# Database connection
Connection = dbConnect(odbc(),Driver = "Sql Server",Server = "inp2300irmadb01\\ntwk", Database = "AKRO")

# Build a query
Sql = "SELECT Identifier
, Deliverable
, [Format]
, Schedule
, Responsibility
, Convert(Varchar(2000),[Description]) as [Description]
, Convert(Varchar(2000),Specifications) as Specifications
, Convert(Varchar(2000),FileNamingScheme) as FileNamingScheme
, Convert(Varchar(2000),DataHandling) as DataHandling
, Convert(Varchar(2000),QAQC) as QC
, Convert(Varchar(2000),Archival) as Archival
, Convert(Varchar(2000),BuilderTasks) as BuilderTasks
, Convert(Varchar(2000),ValidatorTasks) as ValidatorTasks
, Convert(Varchar(2000),CertifierTasks) as CertifierTasks
, [Version], ProtocolID
, SOP, SOPVersion,DeliverableID, VSID, NetworkID
FROM vwDeliverablesSchedule2
WHERE (ProtocolID = 35)
ORDER BY Identifier"

# Execute the query
data = dbGetQuery(Connection,Sql)

```

The National Park Service's Western Yellow-billed Loons monitoring program will collect and maintain the following data deliverables. 
Each mandatory deliverable should be fulfilled during a survey and delivered to the ARCN data manager for integration with the 
master loons monitoring SQL Server database and the [NPS Data Store](https://irma.nps.gov/DataStore/Reference/Profile/2216938).

```{r,echo=FALSE}
knitr::kable(data %>% select(Identifier,Deliverable))

```

```{r,echo=FALSE,results='asis'}
for(i in 1:nrow(data)){
  Identifier = data[i,'Identifier']  
  Deliverable = data[i,'Deliverable']  
  Format = data[i,'Format']  
  Schedule = data[i,'Schedule']  
  Responsibility = data[i,'Responsibility']  
  Description = data[i,'Description']  
  Specifications = data[i,'Specifications']  
  FileNamingScheme = data[i,'FileNamingScheme']  
  DataHandling = data[i,'DataHandling']  
  QC = data[i,'QC']  
  Archival = data[i,'Archival']  
  BuilderTasks = data[i,'BuilderTasks']  
  ValidatorTasks = data[i,'ValidatorTasks']  
  CertifierTasks = data[i,'CertifierTasks']  
  Version = data[i,'Version']  
  ProtocolID = data[i,'ProtocolID']  
  SOP = data[i,'SOP']  
  SOPVersion = data[i,'SOPVersion']  
  DeliverableID = data[i,'DeliverableID']  
  VSID = data[i,'VSID']  
  NetworkID = data[i,'NetworkID']

  cat("# ",Identifier,": ",Deliverable,"  \n\n",sep="")
  cat("*Format:* ",Format,"  \n\n",sep="")  
  cat("*Schedule:* ",Schedule,"  \n\n",sep="")  
  cat("*Responsibility:* ",Responsibility,"  \n\n",sep="")  
  cat("*Description:* ",Description,"  \n\n",sep="")  
  cat("*Specifications:* ",Specifications,"  \n\n",sep="")  
  cat("*FileNamingScheme:* ",FileNamingScheme,"  \n\n",sep="")  
  # cat("*DataHandling:* ",DataHandling,"  \n\n",sep="")  
  # cat("*QC:* ",QC,"  \n\n",sep="")  
  # cat("*Archival:* ",Archival,"  \n\n",sep="")  
  # cat("*BuilderTasks:* ",BuilderTasks,"  \n\n",sep="")  
  # cat("*ValidatorTasks:* ",ValidatorTasks,"  \n\n",sep="")  
  # cat("*CertifierTasks:* ",CertifierTasks,"  \n\n",sep="")  
  # cat("*Version:* ",Version,"  \n\n",sep="")  
  # cat("*ProtocolID:* ",ProtocolID,"  \n\n",sep="")  
  # cat("*SOP:* ",SOP,"  \n\n",sep="")  
  # cat("*SOPVersion:* ",SOPVersion,"  \n\n",sep="")  
  # cat("*DeliverableID:* ",DeliverableID,"  \n\n",sep="")  
  # cat("*VSID:* ",VSID,"  \n\n",sep="")  
  # cat("*NetworkID:* ",NetworkID,"  \n\n",sep="") 
  cat("  \n\n")
}

# for(Col in colnames(data)){
#   # cat(Col," = data[i,'",Col,"']  \n",sep="")
#   cat("cat(\"*",Col,":* \",",Col,",\"  \\n\\n\",sep=\"\")  \n",sep="")
# }

```
